### 2012-06-20 inst/examples/value_of_information.Rmd
Sethi with uniform noise, logistic map

`ro cache=TRUE, warning=FALSE, comment=NA, message=FALSE, cache.path="value_of_information/", verbose=TRUE or`

@@

@@

  z_g <- function() rlnorm(1,  0, policy_g) 
  z_m <- function() rlnorm(1,  0, policy_m) 
  z_i <- function() rlnorm(1,  0, policy_i)

@@

``` {r runall}
det <- scenario(0, 0.0, 0.0)
g <- scenario(0.2, 0.0, 0.0)
m <- scenario(0.0, 0.2, 0.0)
i <- scenario(0.0, 0.0, 0.2)
gm <- scenario(0.2, 0.2, 0.0)
gi <- scenario(0.2, 0.0, 0.2)
gmi <- scenario(0.2, 0.2, 0.2)
````

@@

``` {r runallsims, dependson="simfn"} 
policyfn <- list(det=det, g=g, m=m, i=i, gm=gm, gi=gi, gmi=gmi)
noise <- list(s0=c(0,0,0), sg=c(.2, 0, 0), sm=c(0, .2, 0), si=c(0,0,.2), sgm=c(.2, .2, 0), sgi=c(.2, 0, .2), sgmi=c(.2, .2, .2)) 
allcases <- lapply(policyfn, function(policyfn_i){
  lapply(noise, function(noise_i){
    simulatereps(policyfn_i, noise_i[1], noise_i[2], noise_i[3])
  })
})
````

>>>>

`ro cache=TRUE, warning=FALSE, comment=NA, message=FALSE, cache.path="value_of_information_symmc/", verbose=TRUE or`

@@

**Test with symmetric noise functions**

@@

  z_g <- function() rnorm(1,  0, policy_g) 
  z_m <- function() rnorm(1,  0, policy_m) 
  z_i <- function() rnorm(1,  0, policy_i)

@@

``` {r runall}
lvl <- 0.1
det <- scenario(0, 0.0, 0.0)
g <- scenario(lvl, 0.0, 0.0)
m <- scenario(0.0, lvl, 0.0)
i <- scenario(0.0, 0.0, lvl)
gm <- scenario(lvl, lvl, 0.0)
gi <- scenario(lvl, 0.0, lvl)
gmi <- scenario(lvl, lvl, lvl)
````

@@

``` {r runallsims, dependson="simfn"} 
policyfn <- list(det=det, g=g, m=m, i=i, gm=gm, gi=gi, gmi=gmi)
noise <- list(s0=c(0,0,0), sg=c(lvl, 0, 0), sm=c(0, lvl, 0), si=c(0,0,lvl), sgm=c(lvl, lvl, 0), sgi=c(lvl, 0, lvl), sgmi=c(lvl, lvl, lvl)) 
allcases <- lapply(policyfn, function(policyfn_i){
  lapply(noise, function(noise_i){
    simulatereps(policyfn_i, noise_i[1], noise_i[2], noise_i[3])
  })
})
````
